\documentclass[a4paper,10pt]{article} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
%\setmainfont{Fontin Regular}[SmallCapsFont = Fontin SmallCaps]
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin Regular}

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{multicol}
\usepackage{ragged2e}
\usepackage{array}
\usepackage{booktabs}
\usepackage{color}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{multirow}
\pagestyle{empty} % Removes page numbering

\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$-$}

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section
%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
	\parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
		\begin{shaded}
			\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
		\end{shaded}
	}\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
\color{blue}
\section{Selected Projects}
\color{Black}
\begin{itemize}
	\item \textcolor{blue(ryb)}{Freelancer}:
		\begin{itemize}
			\item 
				\textbf {Trip Assistant:} Implementation of Telegram bot listing airlines, trains, buses, and hotels available seats (or rooms) from multiple sources.
			\item
				\textbf {Instagram Follower:} Implementation of a bot following, unfollowing users automatically in order to gather followers.
			\item
				\textbf{Java Class Loader:} Implementation of an application modifying Java Class loader to load classes from encrypted jars at runtime.
			\item
				\textbf{In-memory executor:} Implementation of a system decrypting encrypted byte code in heap memory, finding main method address in heap and executing it using pure C and Linux Kernel System Calls. \\
			
		\end{itemize}
	
	\item \textcolor{blue(ryb)}{Hobby}:
		\begin{itemize}
			\item
			\textbf {Quote manager:} Implementation of cloud system storing favorite verse, quote, book info, and summary.
			
			\item 
				\textbf{Tiny Controller:} Implementation of simplified Openflow Controller, supporting Hello, EchoReq, EchoRes, FeatureReq, PacketIn, and PacketOut packets.
							
			\item 
				\textbf{Digistyle:} Implementation of a bot finding lowest price clothe on Digistyle site using NodeJS.
				
			\item 
				\textbf{TextBook RSA:} Implementation of simple asymmetric encryption algorithm\\
			
		\end{itemize}
	
	\item \textcolor{blue(ryb)}{Course projects} :
	\begin{itemize}
		\item
			\textbf{Smart Parking System} \hfill \textbf{Internet Engineering} \\
% 			In Internet engineering course we devided into groups and each group defined IoT project for himself. We choose Smart parking which shows Parking lot status to users (Empty, Available, or Reserved). In first phase of project we detect car with Ultrasonic and send it through Bluetooth to Android app (Used arduino nano to connect bluetooth and Ultrasonic modules). In second phase we used nodeMCU modules to connect Ultrasonic through Wifi to server and show car status online. In last phase we connected mobile app to server.
			Design and Implementation of a system with two versions. One detects parking lot status (Empty, Available, or Reserved) via Ultrasonic, sends the data to Android app through Bluetooth. The other makes use of nodeMCU module to connect Ultrasonic through Wifi to cloud server and shows lot status through web browser and mobile apps (iOS and Android) \\
			Technologies: Android, Java, NodeJS 
		
		\item
			\textbf{TCP over UDP} \hfill \textbf {Computer Network} \\
			Implementation of TCP protocol over UDP socket with features like Gurantee data integrity, Congestion Control, and Connection.\\
			Technologies: Java
			
			
		\item
			\textbf {Sara HTTP Proxy} \hfill \textbf {Computer Network} \\
			Implementation of a proxy caching GET method of users http requests in order to reduce response time. \\
			Technologies: Java, Raw Sockets
		
		\item
			\textbf{Load-balance Controller} \hfill \textbf {Computer Network Lab} \\
			Implementation of load balancer controller which round-robin between switches to increase throughput \\
			Technologies: Floodlight Controller, Openflow
			
		\item
			\textbf{Sara Protocol} \hfill \textbf {Computer Network} \\
			Implementation of the protocol detecting network topology with multiple broadcast \\
			Technologies: Floodlight Controller, Openflow
		
		\item
			\textbf{CPU Design} \hfill \textbf {Computer Architecture Lab} \\
			Implementation of Mips CPU's instruction set \\
			Technologies: Verilog , FPGA
			
		\item
			\textbf {Wrist App} \hfill \textbf {Microprocessor} \\
			Design an application controlling step motor with Android App through Bluetooth.\\
			Technologies: ATmega16, Android, Step Motor Driver
		
		\item
			\textbf {PID Logger} \hfill \textbf {Operating System} \\
			Implementation of extra System Calls to Linux OS to List process PIDs. \\
			Technologies: C, Linux
				
		\item
			\textbf{Steganography} \hfill \textbf {Signal and Systems} \\
			Concealing a low resolution picture in high resolution picture \\
			Technologies: MATLAB
			
		
	\end{itemize}

	
\end{itemize}

\end{document}